Reduction, visualization and classification

### 2023-05-23 course/csic5011/2023/project1/1.rebuttal/HUANG_XIA_LUO_Rebuttal-project1-group09.txt

To DUNDA, Gerry Windiarto Mohamad:

Thanks for your kind suggestions. 
For the explanation on the description of SNP dataset, since the background of SNPs dataset including the meaning of SNPs statistics has been 
described clearly in the project requirement file, we simplify this part due to the limited size of poster and focus on the methodology and result analysis. 
Due to the limited size, some details about data analysis such as proportion of train-valid-test, choice of hyperparameters and data preprocessing are not included in the poster, 
we strongly recommend interested readers to read the descriptions in our source files.

In addition, it would be better to include discussions on potential limitations and further analyze the representativeness of SNPs dataset 
and the statistical assumptions of different data reduction methods. We will make improvements on this part.

----------------------------------------------------------
To Shen Lue:

Thanks for your careful review and suggestions! Below are our answers to your review opinions.

1. Answer to "Only uses region-level labels, while the dataset contains 4 granualarity levels.":
We have two reasons to not consider the other three labels. 
The first one is that we have already got supportive conclusion on this single kind of labels, while the other three labels would give similar result of the general migration trend. 
The second one is that we believe different labels can have different aspects, instead of using all of them to assist each other and get a same general conclusion. 
Therefore, in our case study, we did a more precise analysis with the population label solely on the East Asia area, which can show the value of other labels.

2. Answer to "Methodology part can be explained in a more detailed way.":
Since this is a poster and we focus on addressing the scientific questions, we have given the basic clear description of the methods in use, 
and also there is no more space for more detailed explanation (I guess you mean equations etc.). 
Furthermore, we provided references for all the methods mentioned in the poster. If the readers are interested they may refer to the reference for details themselves.

3. Answer to "Did not analyse the geographic variations on the results from PCA/MDS and random projections.":
Yes we did not include this conclusion, and we will try to add it. 
The main reason that we omitted it previously is that we think this conclusion has been covered in our lecture, but we will add it to make this poster an independent and complete work.

4. Answer to "Only uses random projections on PCA, but does not apply for MDS.":
We think it is not so necessary to apply random projections on MDS, for the same reason as "only use region-level labels"

5. For the other small issues, like the HKUST logo and code comments, we will make modifications on them.

----------------------------------------------------------
To HU Yueying:

Thanks for your comments. 
We are sorry that as the size of poster is limited, though we want to include more information and more detailed descriptions, 
we have to reduce the figure size and omit their captions otherwise the space will not be enough. 
We will choose vector diagram and pay more attention to typesetting and formats.

----------------------------------------------------------
To LIN Hangyu:

Thanks for your advice. 
Though some conclusions are qualitative, they are actually drawn from the qualitative analysis on the dataset. 
If the poster size allows, we would like to include the quantitative information about those results for better illustrations.

----------------------------------------------------------
To Ningyu Yan:

Thanks for your attention. Due to the limited space of the poster, we can only prioritize the important information, 
perhaps writing a report contained more analysis of weakness is the best choice.

----------------------------------------------------------
To Bokai Yan:

Thanks for your acvice. We really want to explain every details about figures, but we can not balance the space and information.
If you are interested in details, we are happy to write you a report to give a further explaination.

----------------------------------------------------------
To Zhiwei Wang:

Thanks for your comments. Due to time constraints, we only tested tree methods with 5-fold test and did not do strict statistical tests.
The random forest method is confirmed to be feasible, which is shown in several papers, but for completeness we should add some cross-validation methods, 
or verify on other data sets.

----------------------------------------------------------
To Huang Zhi:

Thank you for your advice! 
We have omitted the figure caption due to the limited space, which may cause some unclear pointing to the figures in the current version, 
but there is no missing figures mentioned in the context. We will revise the figure caption to make it more readable. 
Moreover, we will improve the conclusion part by putting the specific results into it and check the grammar whether there is some.

---------------------------------------------------------
To Ruan Yuyan:

Thank you for your opinion!
With the dataset of 1064 people, we have already got a solid and obvious conclusion from our analysis using multiple methods. 
Analyzing on a larger dataset would definitely give a better conclusion and generalization, but 1064 people are all the information in the dataset given here.

### 2023-05-23 course/csic5011/2023/project1/1.rebuttal/SHEN_rebuttal.md

# Rebuttal

Thanks for your reading and all of your review comments! Here are my feedbacks.

> CUI Yifan:
>
> 1. K-means method is used without theoretical background description or proper citation and
> 2. the number of pages exceeds the maximum requirement.

Regarding the use of the k-means method, I apologize for not providing a more detailed theoretical background description or proper citation. I will revise the manuscript to provide a more thorough explanation of the method and appropriate citations.

Regarding the length of the paper, I acknowledge that it exceeds the maximum requirement. However, I believe that the additional information and analysis provided in the paper are necessary for a comprehensive understanding of my findings. I will work to condense the paper while still ensuring that all relevant information is included. Thanks for your feedback.

> Gerry DUNDA:
>
> - The paper does not discuss the limitations of the statistical methods used for the analysis, such as PCA, MDS, and t-SNE. While these methods can be powerful tools for exploring high-dimensional data, they have certain assumptions and limitations that may affect their results.

I agree that every statistical method has its own assumptions and limitations, including PCA, MDS, and t-SNE. In my paper, I did mention some limitations of the data and methods used, such as the small sample size and potential biases in the data collection. However, I acknowledge that more discussion on the limitations of the statistical methods could have been included. Regarding the limitations of PCA, I am aware that PCA assumes a linear relationship between variables, and it may not be the most suitable method for non-linear data. Also, the interpretation of the principal components may not always be straightforward, and there could be noise in the data that affects the results. Similarly, MDS and t-SNE have their own assumptions and limitations, such as the choice of distance metrics and the effects of noise and outliers. I could have discussed these limitations in more detail, and I appreciate your feedback on this. Thanks for your feedback and I will keep this in mind for future research.

> HUANG Zhanmiao:
>
> - The contents and explored questions are relatively basic and simple. The investigation can go deeper.

While I agree that further investigations can always be conducted, I believe that my study provides valuable insights into the migration patterns and genetic diversity of human populations. I think my work can serve as a foundation for future studies to build upon and deepen my understanding of these complex topics.

> LI Yakun:
>
> 1. It would be better if potential limitations of these methods are discussed in the report.
> 2. However, there are some minor typos that could be corrected.

Regarding question 1, please check my feedbacks for Gerry. Thanks.

Regarding question 2, I appreciate your feedback and will carefully review and correct any errors that I find. Thank you for bringing this to my attention.

> LIU Yonglin:
>
> - The report does not discuss potential limitations of the PCA method or the assumptions made during the analysis.

Please check my feedbacks for Gerry. Thanks.

> LUO Yuanhui
>
> - How human migration history is revealed by the relationship between SNPs and geographical information can be clearer.

Regarding the clarity of how human migration history is revealed by the relationship between SNPs and geographical information, I agree that this could be further clarified. In particular, I could provide more detail on the specific SNPs that were found to be informative for inferring population history, and how they relate to known migration events in human history. Additionally, I could provide more detail on the statistical methods used to infer these relationships and how they contribute to our understanding of human migration history. Thanks for your valuable feedback.

> TENG Fei
>
> - It seems that the sample size will affect the experiment result. But there exists few experiments to test relative large sample size.

I appreciate your comment and agree that sample size can have an impact on the results of experiments. In this study, we acknowledge the limitation of our relatively small sample size of 1043 individuals. However, we believe that our results provide valuable insights into human migration history based on the available data. As for experiments with larger sample sizes, I hope that future studies can build upon my work and explore this topic further. Thanks.

> ZHONG Guangzheng:
>
> - The figures should follows the text that they are metioned.

Thanks for your feedback. I have reviewed all figures and their captions, no such issue has been found yet. Please elaborate more if you found any. Thanks.

### 2023-05-23 course/csic5011/2023/project2/Li-Liu-Hao-Hu/Prediction.Rmd
project2

---
title: "project1"
author: "Yifan HAO"
date: "2023-04-04"
output: html_document
---

@@

```{r}
library(R.matlab)
datmat<-readMat("C:/Users/Lenovo/Desktop/project1/snp452-data.mat")

z<-datmat$X
x<-datmat$X[-1,]
for(i in 1:452){
  x[,i]<-diff(z[,i])/z[-1258,i]
}
x<-as.data.frame(x)
y<-as.data.frame(t(array(unlist(datmat$stock),dim = c(3,452))))#name/full name/group
colnames(y)<-c("name","detail","group")
colnames(x)<-y[,1]

@@

```{r}
#bar plot in group
library(ggplot2)
z<-unique(y$group)
n<-length(z)
gp<-rep(0,n)
for(i in 1:n){
  gp[i]<-length(which(y$group==z[i]))
}

@@

```{r}
#ts plot
for(i in 1:10){
  plot(1:1257,as.numeric(x[,target[i]]),type = "l",main = count_bar$group[i])
}
```

```{r}
#heatmap in-group
library(ggcorrplot)
target<-target[-9]
target_gp<-count_bar$group[-9]
h<-matrix(rep(0,452*452),ncol = 452)
for(i in 1:452){
  for(j in i:452){
    h[i,j]<-cor(x[,i],x[,j])
    h[j,i]<-h[i,j]
  }
}

for(i in 1:9){
  index<-which(y$group==target_gp[i])
  plt<-ggcorrplot(h[index,index])
  print(plt)
}
```

@@

```{r}
frst<-function(x,y,pt,fn,bk,dis){ 
#(x,y) is data; pt is the forecasting point; fn is factor number max value; bk is the lag value; dis is the feature distance in different alg 
  t<-length(y)
  lt<-matrix(rep(0,7*(t-pt+1)),ncol = 7)#baseline/pca/spca/tpca-mds/tpca-iso/tpca-tsne/tpca-spca
  ll<-list(lt)
  for(k in 2:fn){
    ll[[k]]<-lt
  }
  if(bk==0){
    bk<-1
    y_bk<-matrix(rep(0,bk*length(y[(bk+1):t])),ncol = bk)
  }else{
    y_bk<-matrix(rep(0,bk*length(y[(bk+1):t])),ncol = bk)
    for(i in 1:bk){
      y_bk[,i]<-y[(bk+1-i):(t-i)]
    }
  }
  for(i in pt:t){
    #print(paste(i,"-th"))
    st<-bk+1+i-pt
    ed<-i-1
    #or
    if(bk>0){
      fit.or<-lm(y[st:ed]~y_bk[(st-bk):(ed-bk),])
      cc<-fit.or$coefficients
      cc[which(is.na(cc))]<-0
      for(bn in 1:fn){
        ll[[bn]][i-pt+1,1]<-sum(c(1,as.matrix(y_bk[i-bk,]))*cc)
      }
    }

@@

@@

```{r}
for(i in 1:9){
  aa<-auto.arima(x[,target[i]],max.p = 20,max.q = 20,max.d = 20,ic="bic")
  print(i)
  print(aa)
}
#get the result that lag==1 is reasonable
```

```{r}
tsne<-read.csv("tsne3.csv")[,-1]
spca<-read.csv("spca3.csv")[,-1]
mds<-read.csv("mds3.csv")[,-1]
iso<-read.csv("iso3.csv")[,-1]
```

```{r}
#total 1257; start from 755(pt == 755, bk == 1
re<-data.frame(matrix(rep(0,7*7*9),ncol = 7))
colnames(re)<-c("baseline","pca","spca","tpca-mds","tpca-iso","tpca-tsne","tpca-spca")
re$fac<-rep(1:7,9)
re$index<-rep(target_gp,each=7)

for(i in 1:9){
  print(i)
  dis<-matrix(c(as.numeric(mds[target[i],-target[i]]),as.numeric(iso[target[i],-target[i]]),as.numeric(tsne[target[i],-target[i]]),as.numeric(spca[target[i],-target[i]])),ncol = 4)
  ll<-frst(as.matrix(x[,-target[i]]),as.numeric(x[,target[i]]),pt=755,fn=7,bk=1,dis = dis)
  for(j in 1:7){
    for(k in 1:7){
      re[(i-1)*7+j,k]<-mean((ll[[j]][,k] - x[755:1257,target[i]])^2)
    }
  }
}
```

```{r}
write.csv(re, file = "mse_result_0.2")
```

>>>>

---
  title: "project1"
author: "Yifan HAO"
date: "2023-05-18"
output: html_document
---

@@

  ```{r}
###data loading
library(fbi)
#md <- fredmd(file = "monthly.csv", transform = TRUE)
qd <- fredqd(file = "quarterly.csv",transform = TRUE)
#View(md)
View(qd)
qd_dis<-fredqd_description
#md_dis<-fredmd_description

for(i in 2:247){
  aa<-which(is.na(qd[61:252,i]))
  if(length(aa)>0){
    print("r.v")
    print(i)
    print(aa+60)
  }
}

#remove 22,76,92,135,138,142,168,179,180,182,188,232
#from 1974Q1 to 2021Q4
#total: 192 variables number: 235-1=234
qdt<-qd[61:252,-c(22,76,92,135,138,142,168,179,180,182,188,232)]

for(i in 2:234){
  qdt[which(is.na(qdt[,i])),i]<-0
}

am<-as.matrix(qdt[,-1])
aa<-svd(am%*%t(am))
ald<-aa$d[1:191]/aa$d[2:192]
print(ald[1:20])

@@

```{r}
#bar plot in group
ql<-colnames(qdt)[-1]
qid<-qd_dis$group[1:234]
for(i in 1:234){
  # print(i)
  s<-qd_dis$group[which(qd_dis$fred==ql[i])]
  if(length(s)>0){
    qid[i]<-s
  }

}

```{r}
name_gp<-data.frame("index"=ql,"group"=qid)
write.csv(name_gp,file = "index-group.csv")
```

```{r}
#bar plot in group
library(ggplot2)
z<-unique(qid)
n<-length(z)
gp<-rep(0,n)
for(i in 1:n){
  gp[i]<-length(which(qid==z[i]))
}

@@

@@

  ```{r}
frst<-function(x,y,pt,fn,bk,dis){ 
  #(x,y) is data; pt is the forecasting point; fn is factor number max value; bk is the lag value; dis is the feature distance in different alg 
  t<-length(y)
  lt<-matrix(rep(0,9*(t-pt+1)),ncol = 9)#baseline/pca/spca/tpca-mds/tpca-iso/tpca-tsne/tpca-spca/tpca-rpca/tpca-lle
  ll<-list(lt)
  for(k in 2:fn){
    ll[[k]]<-lt
  }
  if(bk==0){
    bk<-1
    y_bk<-matrix(rep(0,bk*length(y[(bk+1):t])),ncol = bk)
  }else{
    y_bk<-matrix(rep(0,bk*length(y[(bk+1):t])),ncol = bk)
    for(i in 1:bk){
      y_bk[,i]<-y[(bk+1-i):(t-i)]
    }
  }
  for(i in pt:t){
    #print(paste(i,"-th"))
    st<-bk+1+i-pt
    ed<-i-1
    #or
    if(bk>0){
      fit.or<-lm(y[st:ed]~y_bk[(st-bk):(ed-bk),])
      cc<-fit.or$coefficients
      cc[which(is.na(cc))]<-0
      for(bn in 1:fn){
        ll[[bn]][i-pt+1,1]<-sum(c(1,as.matrix(y_bk[i-bk,]))*cc)
      }
    }

@@

    #tpca-rpca
    para.tpca<-sele.tpca(y[st:ed],t(as.matrix(x[(st-1):(ed-1),])),as.matrix(x[i-1,]),nf=fn,dis = dis[,5])
    for(bn in 1:fn){
      if(bn==1){
        fit.tpca<-lm(y[st:ed]~para.tpca$x.in[1,]+y_bk[(st-bk):(ed-bk),])
      }else{
        fit.tpca<-lm(y[st:ed]~t(para.tpca$x.in[1:bn,])+y_bk[(st-bk):(ed-bk),])
      }
      cc<-fit.tpca$coefficients
      cc[which(is.na(cc))]<-0
      #print("cc-spca")
      ll[[bn]][i-pt+1,8]<-sum(c(1,as.numeric(para.tpca$x.out[1:bn,]),as.numeric(y_bk[i-bk,]))*cc)
    }
    #print("tpca")

    #tpca-lle
    para.tpca<-sele.tpca(y[st:ed],t(as.matrix(x[(st-1):(ed-1),])),as.matrix(x[i-1,]),nf=fn,dis = dis[,6])
    for(bn in 1:fn){
      if(bn==1){
        fit.tpca<-lm(y[st:ed]~para.tpca$x.in[1,]+y_bk[(st-bk):(ed-bk),])
      }else{
        fit.tpca<-lm(y[st:ed]~t(para.tpca$x.in[1:bn,])+y_bk[(st-bk):(ed-bk),])
      }
      cc<-fit.tpca$coefficients
      cc[which(is.na(cc))]<-0
      #print("cc-spca")
      ll[[bn]][i-pt+1,9]<-sum(c(1,as.numeric(para.tpca$x.out[1:bn,]),as.numeric(y_bk[i-bk,]))*cc)
    }
    #print("tpca")

@@

```{r}
#mds iso tsne spca rpca lle

#iso 3 lle 3 rpca 3 
#mds_dis1<-read.csv("mds-dist-2pc.csv")[,-1]
dis_mds<-read.csv("mds-dist-4pc.csv")[,-1]
#mds_dis3<-read.csv("mds-dist-6pc.csv")[,-1]

#iso_dis1<-read.csv("isomap-dist-2pc.csv")[,-1]
#iso_dis2<-read.csv("isomap-dist-4pc.csv")[,-1]
dis_iso<-read.csv("isomap-dist-6pc.csv")[,-1]

dis_spca<-read.csv("spca-dist-2pc.csv")[,-1]
#spca_dis2<-read.csv("spca-dist-4pc.csv")[,-1]
#spca_dis3<-read.csv("spca-dist-6pc.csv")[,-1]

#rpca_dis1<-read.csv("rpca-dist-2pc.csv")[,-1]
#rpca_dis2<-read.csv("rpca-dist-4pc.csv")[,-1]
dis_rpca<-read.csv("rpca-dist-6pc.csv")[,-1]

#lle_dis1<-read.csv("lle-dist-2pc.csv")[,-1]
#lle_dis2<-read.csv("lle-dist-4pc.csv")[,-1]
dis_lle<-read.csv("lle-dist-6pc.csv")[,-1]

dis_tsne<-read.csv("tsne-dist-2pc.csv")[,-1]

```{r}
#start from 1974q1 (pt:61  total:192
#target method
#gdp:1; indpro:21; hwi:207; dfs: 114
target<-c(2,22,208,115)

re<-data.frame(matrix(rep(0,4*7*9),ncol = 9))
colnames(re)<-c("baseline","pca","spca","tpca-mds","tpca-iso","tpca-tsne","tpca-spca","tpca-rpca","tpca-lle")
re$fac<-rep(1:7,4)
re$index<-rep(colnames(qdt)[target],each=7)

for(i in 1:4){
  print(i)
  dis<-matrix(c(as.numeric(dis_mds[target[i],-target[i]]),as.numeric(dis_iso[target[i],-target[i]]),as.numeric(dis_tsne[target[i],-target[i]]),as.numeric(dis_spca[target[i],-target[i]]),as.numeric(dis_rpca[target[i],-target[i]]), as.numeric(dis_lle[target[i],-target[i]])),ncol = 6)

  ll<-frst(as.matrix(qdt[,-c(1,target[i])]),as.numeric(qdt[,target[i]]),pt=61,fn=7,bk=1,dis = dis)
  for(j in 1:7){
    for(k in 1:9){
      re[(i-1)*7+j,k]<-mean((ll[[j]][,k] - qdt[61:192,target[i]])^2)
    }
  }

}

```{r}
write.csv(re,file="final_mse.csv")
```

```{r}
library(ggplot2)

i<-1

nm<-c("pca","tpca-iso","tpca-rpca","tpca-lle")

dd1<-data.frame("x"=rep(1:7,4),"y"=as.numeric(unlist(re[((i-1)*7+1):(i*7),c(2,5,8,9)])),"method"=rep(nm,each=7))
ggplot(dd1,aes(x=x,y=y,colour=method))+geom_point()+geom_line()+labs(x="factor number",y="MSE")+ggtitle(paste0("Label: ",re$index[i*7]))
```
